Semi-supervised author disambiguation of scientific publications

### 2015-07-16 paper.tex
Adding content to Overview section

\subsection{Overview}
% figure, notations, etc

>>>>

\subsection{Overview}
% figure, notations, etc
Before presenting the methodology, we need to define some terminologies we will use to describe the data entities. An author's full name, or author name, is the string variation that was mention in the database record to refer to the author. The full name is a composition of the author last name and the author other names. For example, in the full name (Kerth, Leroy T.), the last name is Kerth and the other names will be (Leroy T.). We also use the terminology initials. In our full name example, the initials will be (L T). First initial then will be (L). So, grouping publications  What we refer to as the real author is the real person behind the publication. We will use the term signature as the entity that we apply clustering on.  A signature is a unique combination between a publication and an author name as mentioned in the database. The term blocking means grouping the signature by a certain version of the author name. For example, blocking by the author last name and first name initial means grouping together all signatures that have in common the same author's last name and first name initial. In our example, grouping by the string (Kerth L). What we mean by claimed publications is the publications in which their real author identity were claimed. We use these claimed publications to generate our ground truth data.

Our methodology consists in 4 main components: Distance learning, blocking, semi-supervised clustering and matching. A distance function is learned from a training set of signiture pairs sampled from ground-truth data. Each pair is labeled whether the 2 signatures are for the same real author or not. The learned distance function will then be used for computing the dissimilarity matrix of a block of signatures. A block of signatures is grouping signatures that have in common similar author names, for example same last name. This affinity matrix would be the main input of our semi-supervised clustering algorithm. The predicted clusters of each block will lastly be combined into a final predicted clusters result. Each cluster label represents the predicted single author of the publications in the cluster. Finally, we present a strategy for matching the predicted results with the publications in which their authors were claimed.
